\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-13 paper/paper.tex
Modified abstract

\bigskip
\begin{abstract}
Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  Products with long lifetimes produce few observed failures; and when products do fail the cause of failure is often unknown.  While computationally convenient, simple parametric models are often limited in modeling this type of data.  Small sample sizes make parameter estimates unstable or difficult to obtain.  Multiple failure modes cause bends in the lifetime distribution single parametric models cannot capture.

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model \citep{chan}. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  an early failure due to "infant mortality" and a second failure mode due to wearout. We fit the GLFP model using a hierarchical Bayesian approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using a Bayesian approach, comparison of different product brands is straightforward as estimation of arbitrary functionals are easily computable from the full posterior distribution.
\end{abstract}

>>>>

\bigskip
\begin{abstract}
% Consumers have an interest in accurate assessment of product reliability.  However, lifetime data is often sparse and has limited information.  
While reliability is an important aspect of product quality, by its nature, the lifetime data available to consumers tends to be limited; high-reliability consumer products fail infrequently. Due in part to multiple causes of failure, simple parametric models have limited application, being unable to capture relevant lifetime characteristics. On the other hand, more suitable models are difficult to fit because of small sample sizes. If it were available, failure analysis mitigate identifiability issues; however, consumers do not have this information, nor is it have practical value for them.

In this paper we present a method for joint estimation of multiple lifetime distributions based on the Generalized Limited Failure Population (GLFP) model \citep{chan}. This 5-parameter model for lifetime data accommodates lifetime distributions with multiple failure modes:  early failure due to "infant mortality" and failure due to wearout. We fit the GLFP model using a hierarchical Bayesian approach.  Borrowing strength across populations, our method enables estimation with uncertainty of lifetime distributions even in cases where the number of model parameters is larger than the number of observed failures.  Moreover, using a Bayesian approach, comparison of different product brands is straightforward as estimation of arbitrary functionals are easily computable from the full posterior distribution.
\end{abstract}
